Documentation/overview Functional Limits of Agreement

### 2021-06-10 floa_doc.Rmd
Flowchart old algorithm added

>>>>

#### Eingereichte Version (problematisch)

```{r echo = FALSE, warning = FALSE, message = FALSE}
library(DiagrammeR)

# (Nested) Randomized Cluster Bootstrap
#
# In the first stage (draw_clusters()), all curves of a single (random) subject
# are drawn. From this set, the (functional) mean is calculated. The process is
# repeated n.boot times (n.boot = number of bootstrap iterations)

grViz("digraph flowchart {

      # node definitions with substituted label text
      node [fontname = Helvetica, shape = rectangle]        
      tab1 [label = '@@1']
      tab2 [label = '@@2']
      tab3 [label = '@@3']
      tab4 [label = '@@4']
      tab5 [label = '@@5']
      tab6 [label = '@@6']
      tab7 [label = '@@7']
      tab8 [label = '@@8']

      # edge definitions with the node IDs
      tab1 -> tab2
      tab2 -> tab3
      tab3 -> tab4
      tab3 -> tab5
      tab3 -> tab6
      tab4 -> tab7
      tab4 -> tab8
      }

      [1]: 'Time normalize curves of IMU - MC'
      [2]: 'Create difference curves IMU - MC'
      [3]: 'Convert difference curves to function data objects using Fourier series'
      [4]: 'floa_rcb '
      [5]: 'FLOAboot_2SD '
      [6]: 'floa_point'
      [7]: 'First stage'
      [8]: 'Second stage'
      ")

```

#### Vorschlag für verbesserte Variante
